%for a more compact document, add the option openany to avoid
%starting all chapters on odd numbered pages
\documentclass[12pt]{cmuthesis}

% This is a template for a CMU thesis.
% The source for this is pulled from a variety of sources and people.
% Here's a partial list of people who may or may have not contributed:
%
%        bnoble   = Brian Noble
%        caruana  = Rich Caruana
%        colohan  = Chris Colohan
%        jab      = Justin Boyan
%        josullvn = Joseph O'Sullivan
%        jrs      = Jonathan Shewchuk
%        kosak    = Corey Kosak
%        mjz      = Matt Zekauskas (mattz@cs)
%        pdinda   = Peter Dinda
%        pfr      = Patrick Riley
%        dkoes    = David Koes

% some useful packages
\usepackage{times}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[numbers,sort]{natbib}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
%\usepackage{subfigure}
\usepackage{braket}

% Approximately 1" margins, more space on binding side
%\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar]{geometry}
%for general printing (not binding)
\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar,hmarginratio=1:1]{geometry}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

% Provides a draft mark at the top of the document.
\draftstamp{\today}{DRAFT}

\usepackage{cleveref}
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}
\crefname{section}{Section}{Sections}
\Crefname{section}{Section}{Sections}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}
\crefname{chapter}{Chapter}{Chapters}
\Crefname{chapter}{Chapter}{Chapters}
\usepackage{notoccite}

\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{subcaption}
\captionsetup[subfigure]{format=hang}
\usepackage{wrapfig}
\usepackage{comment}
%\usepackage{setspace}
%\setstretch{1}


\newcommand{\observeab}{Observe$_{ab}$}
\newcommand{\observec}{Observe$_{c}$}
\newcommand{\orientdecide}{Orient+\allowbreak Decide$_{d}$}
\newcommand{\acte}{Act$_{e}$}
\newcommand{\actfg}{Act$_{fg}$}

\setlength{\parskip}{5pt plus 1pt minus 1pt}%

\newenvironment{captext}{%
   \begin{center}%
     \begin{minipage}{0.95\linewidth}%
       \renewcommand{\baselinestretch}{0.8}%
         \footnotesize\centering}%
   {\renewcommand{\baselinestretch}{1.0}%
      \end{minipage}%
        \end{center}}

\begin {document}
\frontmatter

%initialize page style, so contents come out right (see bot) -mjz
\pagestyle{empty}

\title{ %% {\it \huge Thesis Proposal}\\
{\bf Analyzing the OODA Loop of an Edge-enabled Autonomous Drone System}}
\author{Aditya Chanana}
\date{December 18}
\Year{2024}
\trnumber{}

\committee{
Mahadev Satyanarayanan, Chair \\
Padmanabhan Pillai\\
}

\support{}
\disclaimer{}

% copyright notice generated automatically from Year and author.
% permission added if \permission{} given.

\keywords{edge computing, drones, mobile networks, latency, bandwidth, edge-native applications, computer vision, machine learning}

\maketitle

\begin{dedication}
    Dedicated to my family and girlfriend, for their belief in me.
\end{dedication}

\pagestyle{plain} % for toc, was empty

%% Obviously, it's probably a good idea to break the various sections of your thesis
%% into different files and input them into this file...

\begin{abstract}

    The "Observe, Orient, Decide, Act" (OODA) loop encapsulates the agility of
    cyber-physical or cyber-human systems that depend on continuous iterations
    of these steps. Systems with faster OODA loops react more quickly to
    changes in their environment. This work analyzes the OODA loop of the
    SteelEagle edge-enabled autonomous drone system, identifying bottlenecks
    and opportunities for optimization.
    We also analyze the use of onboard computation with SteelEagle, showing how
    to combine the use of onboard computational abilities, for tasks that
    benefit immensely from a faster OODA loop, and offloading, for tasks that
    are more computationally expensive, leading to an optimal system that
    excels in real-time active vision tasks.

\end{abstract}

\begin{acknowledgments}

    Thank you to my research advisors Dr. Mahadev Satyanarayanan and Dr.
    Padmanabhan Pillai for their guidance and feedback on this project, and
    Thomas Eiszler Jr.  and Mihir Bala for their mentorship.  I would like to
    express my gratitude to my parents, Dr. Rashmi Chanana and Sanjay Chanana,
    who have offered their unwavering love, encouragement, and support at every
    stage of my life.  Thank you to my girlfriend, Isabella Wegner, for your
    belief in me.  I am grateful to my academic advisor Dr. David A. Eckhardt
    for being a reliable source of excellent advice, and his encouragement for
    me to pursue research.

    This material is based upon work supported by the U.S. Army Research Office
    and the U.S. Army Futures Command under Contract No. W519TC-23-C-0003, and
    by the National Science Foundation under grant number CNS-2106862. The
    content of the  information does not necessarily reflect the position or
    the policy of the government and no official endorsement should be
    inferred.

    This work was done in the CMU Living Edge Lab, which is
    supported by Intel, Arm, Vodafone, Deutsche Telekom, CableLabs, Crown
    Castle, InterDigital, Seagate, Microsoft, the VMware University Research
    Fund, IAI, and the Conklin Kistler family fund. Any opinions, findings,
    conclusions or recommendations expressed in this document are those of the
    author and do not necessarily reflect the view of the above funding
    sources.
\end{acknowledgments}


\backrefsetup{disable}
\tableofcontents
\listoffigures

\listoftables
\backrefsetup{enable}

\mainmatter

%% Double space document for easy review:
%\renewcommand{\baselinestretch}{1.66}\normalsize

% The other requirements Catherine has:
%
%  - avoid large margins.  She wants the thesis to use fewer pages,
%    especially if it requires colour printing.
%
%  - The thesis should be formatted for double-sided printing.  This
%    means that all chapters, acknowledgements, table of contents, etc.
%    should start on odd numbered (right facing) pages.
%
%  - You need to use the department standard tech report title page.  I
%    have tried to ensure that the title page here conforms to this
%    standard.
%
%  - Use a nice serif font, such as Times Roman.  Sans serif looks bad.
%
% Other than that, just make it look good...

\input{intro.tex}
\input{background.tex}
\input{drones.tex}
\input{steeleagle-optimization.tex}
\input{voxl.tex}
\input{conclusion.tex}

%\appendix
%\include{appendix}

\backmatter
%\renewcommand{\baselinestretch}{1.0}\normalsize

% By default \bibsection is \chapter*, but we really want this to show
% up in the table of contents and pdf bookmarks.
\renewcommand{\bibsection}{\chapter{\bibname}}
%\newcommand{\bibpreamble}{This text goes between the ``Bibliography''
%  header and the actual list of references}
\bibliographystyle{unsrt}
\bibliography{register} %your bib file

% \begin{thebibliography}{00}
%
% \bibitem{thing} thing
%
% \end{thebibliography}

\end{document}
